\documentclass{article}
\usepackage[top=1.0in, bottom=1.0in,left=1.0in, right=1.0in]{geometry}
\usepackage{times}
\renewcommand{\ttdefault}{cmtt}

% sections
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0pt}{0.5em}
\titleformat{\section}{\normalfont\large\sc\bfseries}{}{0em}{}[{\titlerule[0.5pt]}]

% lists
\usepackage{paralist}
\usepackage{enumitem}
\setlist[description]{itemsep=0.2em,style=nextline,labelsep=\parindent,leftmargin=*}
\setlist[itemize]{noitemsep,topsep=0pt}

% title
\makeatletter
\newcommand{\name}[1]{\def\@name{#1}}
\newcommand{\streetaddress}[1]{\def\@streetaddress{#1}}
\newcommand{\citystatezip}[1]{\def\@citystatezip{#1}}
\newcommand{\phone}[1]{\def\@phone{#1}}
\newcommand{\email}[1]{\def\@email{#1}}
\newcommand{\website}[1]{\def\@website{#1}}
\name{}
\streetaddress{}
\citystatezip{}
\phone{}
\email{}
\website{}
\makeatother
\makeatletter
\def\@maketitle{
	\begin{center}
		{\LARGE \bf\@name}\hfill\@streetaddress\\
		\href{mailto:\@email}{\nolinkurl{\@email}}\hfill\@citystatezip\\
		\url{\@website}\hfill\@phone\\
		\vspace{0.25em}
		\hrule height 1pt
	\end{center}
}
\makeatother

% dated entry
\makeatletter
\newcommand{\entry}[1]{\def\@entry{#1}}
\newcommand{\dates}[1]{\def\@dates{#1}}
\entry{}
\dates{}
\newenvironment{datedentry}{\noindent{\bf\@entry}\hfill{\it\@dates\linebreak\/}}{\vspace{0.5em}}
\makeatother

% location entry
\makeatletter
\newcommand{\location}[1]{\def\@location{#1}}
\entry{}
\location{}
\dates{}
\newenvironment{locationentry}{\noindent{\bf \@entry}, \@location\hfill{\it\@dates\linebreak\/}}{\vspace{0.5em}}
\makeatother

% links
\usepackage[dvipsnames]{xcolor}
\usepackage[ocgcolorlinks,urlcolor=violet!85!black]{hyperref}
\urlstyle{same}

\begin{document}

\name{Robert Kernan}
\phone{770\texttt{-}355\texttt{-}4050}
\streetaddress{16 Arbor Way Drive}
\citystatezip{Decatur, GA 30030}
\email{rkernan@gmail.com}
\website{https://github.com/kernan}

\maketitle

\thispagestyle{empty}

% \section{Objective}

\section{Education}

\entry{Georgia Institute of Technology}
\location{Atlanta, GA}
\dates{August 2013}
\begin{locationentry}
	Bachelor of Science in Computer Science \\
	Focus in Information Internetworks and Platforms % \\
	% Major GPA: 3.38 \\
	% Overall GPA: 2.98
\end{locationentry}

\section{Technical Skills}
\begin{description}
	\item[Languages]
		\begin{inparaitem}
			\item C
			\item C++
			\item C\#
			\item Java
			\item Lua
			\item PHP
			\item Python
			\item Ruby
		\end{inparaitem}
	\item[Operating Systems]
		\begin{inparaitem}
			\item Windows 7
			\item GNU/Linux
		\end{inparaitem}
	\item[Software]
		\begin{inparaitem}
			\item Ant
			\item Clang
			\item CMake
			\item Eclipse
			\item GNU Compiler Collection
			\item Make
			\item MySQL
			\item SQLite
			\item Visual Studio
		\end{inparaitem}
	\item[Revision Control]
		\begin{inparaitem}
			\item Git
			\item Mercurial
			\item Subversion
		\end{inparaitem}
\end{description}

\section{Work Experience}

\entry{Noble Systems Corporation}
\location{Atlanta, GA}
\dates{January 2015 -- Present} % chktex 8
\begin{locationentry}
	Quality Assurance Engineer
\end{locationentry}

\entry{Southern Polytechnic State University}
\location{Marietta, GA}
\dates{May 2010 -- July 2010} % chktex 8
\begin{locationentry}
	Lab/Teaching Assistant for CSE 1302: Introduction to Data Structures
	\begin{itemize}
		\item Assigned lab-work and taught supplemental material.
		\item Maintained office hours in the lab for students.
		\item Submitted software requests for lab equipment.
	\end{itemize}
\end{locationentry}

\section{Projects}

\entry{Vector Math Library}
\dates{April 2014 -- Present} % chktex 8
\begin{datedentry}
	\url{https://github.com/kernan/math} \\
	Built and currently maintaining a C++11 header-only library containing
	generic size and type vector and matrix implementations with
	specializations for 2, 3, and 4-dimensions. Includes a unit test suite
	built using Boost.
\end{datedentry}

\entry{Graphics Engine}
\dates{July 2013 -- Present} % chktex 8
\begin{datedentry}
	Building a simple, cross-platform (Windows and Linux currently) graphics
	engine using OpenGL as the rendering backend. Current goals are
	implementing a more advanced input handling system and adding lighting
	primitives to the scene.
\end{datedentry}

\entry{Geopost}
\dates{June 2013 -- August 2013} % chktex 8
\begin{datedentry}
	\url{https://github.com/spardue/geopost} \\
	Designed and developed a REST API for creating geo-tagged content using
	Python.  Collaborated to build an HTML5 front-end that displayed geo-tagged
	content on a map using the Google Maps Javascript API\@.
\end{datedentry}

\entry{Massive Open Online Course (MOOC) Teaching Assistant Manager}
\dates{January 2013 -- April 2013} % chktex 8
\begin{datedentry}
	\url{https://github.com/kernan/MOOC-TA-Management} \\
	Collaborated to design and build a web application for testing and managing
	teaching assistants for MOOCs using Ruby on Rails; utilized Twitter
	Bootstrap to create a reactive front-end. Included a REST API for all
	functionality.
\end{datedentry}

\entry{International Community School Joomla Intranet}
\dates{March 2012 -- May 2012} % chktex 8
\begin{datedentry}
	Collaborate to modify and complete and intranet using Joomla that enabled
	teachers to communicate with students about assignments and upcoming events.
\end{datedentry}

\entry{Parser Generator and Regular Expression Language Interpreter}
\dates{November 2011 -- December 2011} % chktex 8
\begin{datedentry}
	Created scanner, parser, and interpreter in Java for a regular expression
	language that could find, remove, and replace text patterns in a file. The
	scanner and parser tables were not language specific and could be generated
	by feeding the program a context-free grammar.
\end{datedentry}

\end{document}
